Meta-analysis

### 2019-07-23 05_MetaAnalysis.Rmd
Notes, host genotypes and trying to understand generating variance from log ratios... TBC

@@

Now for the trickier part creating 'Sampling Variance from NAs.
```{r}
Trials <- PM_MB_means %>%
   filter(Fungicide == "Tebeconazole",
          row_spacing == 0.75,
          is.na(Y_error.type))

   distinct()
```

>>>>

### Host genotypes
Host genotype may have to be analysed to determine the effect.  
```{r Host_genotype}
PM_MB_means %>%
   filter(Fungicide == "Tebeconazole",
          row_spacing == 0.75) %>% 
   group_by(host_genotype) %>%
   summarise(n = length(host_genotype))

```
In general the mungbean varieties have the following resistance to powdery mildew.  
   - Berken: Highly susceptible  
   - Crystal: Susceptible  
   - Jade: Moderatly susceptible

@@

Now for the trickier part creating 'Sampling Variance' for treatments where only mean yeild is recorded.  
The trial which does not report any type of variance also reports that there is no significant difference between the means.
```{r}
PM_MB_means %>%
   filter(Fungicide == "Tebeconazole",
          row_spacing == 0.75,
          is.na(Y_error.type)) %>%
   select(Trial_ref)%>%
   distinct()
```

A single trial `mung1516/03` within the current scope od the meta-analysis fails to report a varience statistic. According to [Machado F. et. al (2017)](http://apsjournals.apsnet.org/doi/10.1094/PDIS-03-17-0340-RE) [Paul et. al. (2007)](https://apsjournals.apsnet.org/doi/pdfplus/10.1094/PHYTO-97-2-0211) uses linear regression model to estimate sampling variance.

```{r na2Sampling_variance}

for(i in PM_MB_means$Trial_ref){

log(V)[i] = a + b * log(
   mean(subset(PM_MB_means$grain_yield.t.ha.[i], Fungicide == "control"),
        subset(PM_MB_means$grain_yield.t.ha.[i], Fungicide == "Tebeconazole")))
# need to know what parameters a and b are here
# I am guessing they represent prediction parameters for each "study" for each of the treatments, "control" and Tebeconazole"
